\section{Freespace Component}
The freespace component serves as main component in the architecture of the Once Decorator Pattern. It stores fields
variables (arrays for storing $D, E, B, H$) as instance variables and provides the interfaces to update fields by the
rules in freespace. The fields variables are also utilized by concrete decorators which inherit the main component. And
about interfaces, there is a big point here. Comparing the Eq.\ref{eq:pmldx} and Eq.\ref{eq:dx3d}, the curl parts are
are not changed. Apparently it is necessary to provide interfaces for these reusable parts. The $curl\_ex$ and
$curl\_hx$ is a example here.
\begin{code}
    def curl_ex(self):
        res = numpy.zeros(self.shape)
        (x,y,z) = self.shape
        for i in range(x):
            for j in range(y-1):
                for k in range(z-1):
                    res[i,j,k] = self.ezfield[i,j+1,k] - self.ezfield[i,j,k] 
                               - self.eyfield[i,j,k+1] + self.eyfield[i,j,k]
        return res

    def curl_hx(self):
        res = numpy.zeros(self.shape)
        (x,y,z) = self.shape
        for i in range(x):
            for j in range(y):
                for k in range(z):
                    res[i,j,k] = self.hzfield[i,j,k] - self.hzfield[i,j-1,k] 
                               - self.hyfield[i,j,k] + self.hyfield[i,j,k-1]
        return res
\end{code}
The return value is a 2D array saving the values of curl for each point. with thees interfaces, Eq.\ref{eq:dx3d} and
Eq.\ref{eq:bx3d} appear a elegant view in source code.
\begin{code}
    def update_dfield(self):
        self.dxfield += 0.5 * self.curl_hx()
        self.dyfield += 0.5 * self.curl_hy()
        self.dzfield += 0.5 * self.curl_hz()
        return self
    def update_bfield(self):
        self.bxfield -= 0.5 * self.curl_ex()
        self.byfield -= 0.5 * self.curl_ey()
        self.bzfield -= 0.5 * self.curl_ez()
        return self
\end{code}
And the E field and H field are just copied from D and B in freespace. Similar handlers for material are left to
implement in Dispersion concrete decorator to overwrite these two interfaces.
\begin{code}
    def update_efield(self):
        self.exfield = self.dxfield.copy()
        self.eyfield = self.dyfield.copy()
        self.ezfield = self.dzfield.copy()
        return self

    def update_hfield(self):
        self.hxfield = self.bxfield.copy()
        self.hyfield = self.byfield.copy()
        self.hzfield = self.bzfield.copy()
        return self
\end{code}


