\section{TF/SF Component}
Concepts of TF/SF Component are easy to grasp. However, the theory left a big blank canvas for implementation because
there are eight types in two dimension and twelve types in three dimension. A intuitive implementation is categorizing
by incident direction to be XTFSF, YTFSF, and ZTFSF (only in 3D). An XTFSF can be TM or TE mode and each mode can be
rectangle layout or infinite layout working with PBC (Fig.???), YTFSF and ZTFSF too. By example of YTFSF in two
dimension, the constructor appends two auxiliary 1D source as well as masks boundary of TFSF in two direction. 
\begin{code}
    def __init__(self, orig):
        super(YTFSFPlane, self).__init__(orig)
        self.tminc = String(self.shape[1])
        self.teinc = String(self.shape[1])
        self.xtfsf = [10, self.shape[0]-10]
        self.ytfsf = [10, self.shape[1]-10]
        return None
\end{code}
The rest is two more interfaces to insert D and B at TFSF boundary. To simplify, TE and TM mode are inserted at the same
time. If only one mode is needed, no updating on the unnecessary auxiliary 1D source in main script could disable
it. This design leads to more overhead but creates elegant depiction. The next big trick is to examinate whether the
boundaries in x direction are \texttt{[None, None]}. If the assertion is true, regard TFSF itself as a layout infinite
at x direction. Otherwise, it's a rectangle layout should update boundaries in x direction.
\begin{code}
    def update_dtfsf(self):
        if self.xtfsf == [None, None]:
            self.dzfield[:, self.ytfsf[0]]
            += 0.5 * self.tminc.hfield[self.ytfsf[0]-1]
            self.dzfield[:, self.ytfsf[1]] 
            -= 0.5 * self.tminc.hfield[self.ytfsf[1]]
            self.dxfield[:, self.ytfsf[0]]  
            -= 0.5 * self.teinc.hfield[self.ytfsf[0]-1]
            self.dxfield[:, self.ytfsf[1]]  
            += 0.5 * self.teinc.hfield[self.ytfsf[1]]
        else:
            # y edge
            self.dzfield[self.xtfsf[0]:self.xtfsf[1]+1, self.ytfsf[0]]  
            += 0.5 * self.tminc.hfield[self.ytfsf[0]-1]
            self.dzfield[self.xtfsf[0]:self.xtfsf[1]+1, self.ytfsf[1]]  
            -= 0.5 * self.tminc.hfield[self.ytfsf[1]]
            self.dxfield[self.xtfsf[0]:self.xtfsf[1]+1, self.ytfsf[0]]  
            -= 0.5 * self.teinc.hfield[self.ytfsf[0]-1]
            self.dxfield[self.xtfsf[0]:self.xtfsf[1]+1, self.ytfsf[1]]  
            += 0.5 * self.teinc.hfield[self.ytfsf[1]]

            # x edge
            self.dyfield[self.xtfsf[0],   self.ytfsf[0]:self.ytfsf[1]+1] 
            += 0.5 * self.teinc.hfield[self.ytfsf[0]:self.ytfsf[1]+1]
            self.dyfield[self.xtfsf[1]+1, self.ytfsf[0]:self.ytfsf[1]+1] 
            -= 0.5 * self.teinc.hfield[self.ytfsf[0]:self.ytfsf[1]+1]
        return self


    def update_btfsf(self):
        if self.xtfsf == [None, None]:
            # y edge
            self.bxfield[:, self.ytfsf[0]-1]
            += 0.5 * self.tminc.efield[self.ytfsf[0]]
            self.bxfield[:, self.ytfsf[1]]  
            -= 0.5 * self.tminc.efield[self.ytfsf[1]]
            self.bzfield[:, self.ytfsf[0]-1]
            += 0.5 * self.teinc.efield[self.ytfsf[0]]
            self.bzfield[:, self.ytfsf[1]]  
            -= 0.5 * self.teinc.efield[self.ytfsf[1]]
        else:
            # y edge
            self.bxfield[self.xtfsf[0]:self.xtfsf[1]+1, self.ytfsf[0]-1] 
            += 0.5 * self.tminc.efield[self.ytfsf[0]]
            self.bxfield[self.xtfsf[0]:self.xtfsf[1]+1, self.ytfsf[1]]   
            -= 0.5 * self.tminc.efield[self.ytfsf[1]]
            self.bzfield[self.xtfsf[0]:self.xtfsf[1]+1, self.ytfsf[0]-1] 
            += 0.5 * self.teinc.efield[self.ytfsf[0]]
            self.bzfield[self.xtfsf[0]:self.xtfsf[1]+1, self.ytfsf[1]]   
            -= 0.5 * self.teinc.efield[self.ytfsf[1]]

            # x edge
            self.byfield[self.xtfsf[0]-1, self.ytfsf[0]:self.ytfsf[1]+1] 
            -= 0.5 * self.tminc.efield[self.ytfsf[0]:self.ytfsf[1]+1]
            self.byfield[self.xtfsf[1],   self.ytfsf[0]:self.ytfsf[1]+1]
            += 0.5 * self.tminc.efield[self.ytfsf[0]:self.ytfsf[1]+1]
        return self
\end{code}
