\section{Boundary Conditions}
\label{sec:bcs}
Three kinds of boundary conditions (BCs) are applied in this research: Analytic Absorbing Boundary Conditions (ABCs),
Perfectly Matched Layer (PMLs) Absorbing Boundary Conditions and Periodic Boundary Conditions (PBCs). All three kinds of
BCs have the purpose to create a fake infinite space via finite computation domain. One difference is that the ABC and
PML are designed for making only one set of structure appearing in the computation domain rather than place infinite
sets of identical structure like in the PBC.


\subsection{Analytic Absorbing Boundary Conditions}
To hold the outgoing field from being reflected at boundary, the ABC is operative in 1D FDTD lattice. Once we assume
there are no sources outside the computation region, the wave must be porpagaing outward directly and the value of field
at two ends can be estimated with the relation through the Courant Condition.
\begin{equation}
  E|_0^n = E|_1^{n-2}
\end{equation}
\begin{equation}
  E|_k^n = E|_{k-1}^{n-2}
\end{equation}



\subsection{Perfectly Matched Layer Absorbing Boundary Conditions}
\label{subsec:pml}
For 2-D and 3-D simulations, the ABC discussed above is no longer useful due to that the ABC can only absorb normally
incident waves. The Berenger's PML (BPML) [\textit{Berenger} 1994], also known as the Split-Field PML, was firstly
proposed. Then, the Unaxial PML (UPML) [\textit{Sacks et al}, 1995] was proposed with similar performance in mathematics
but different machenism. The two PMLs shown above require free space at the interface of PML. The Convolution PML (CPML)
proposed later allows arbitrary material and performs better on absorbing evanescent wave.

By inserting coefficients of UPML into (\ref{eq:up_d}) and (\ref{eq:up_b}), half of the update equations become what
follows. Owing to that the $\bar{\bar{s}}$ parameters can be reduced to $1$ in non-PML regions, the new update equations
are apt to be applied in the whole computation domain.
\begin{gather}
  j\omega\bar{\bar{s}}\ \widetilde{D}(\omega) = c_0\curlH(\omega)\\
  j\omega\bar{\bar{s}}\ \widetilde{B}(\omega) = -c_0\curlE(\omega)
\end{gather}
where $\bar{\bar{s}}$ should satisfy
\begin{equation}
  \bar{\bar{s}} = 
  \begin{bmatrix}
    \displaystyle\frac{s_ys_z}{s_x}& 0& 0\\
    0& \displaystyle\frac{s_xs_z}{s_y}& 0\\
    0& 0& \displaystyle\frac{s_xs_y}{s_z}
  \end{bmatrix}
\end{equation}
with 
\begin{equation}\label{eq:pmlco}
  s_x = 1 + \frac{\sigma_x}{j\omega\epsilon_0},\ 
  s_y = 1 + \frac{\sigma_y}{j\omega\epsilon_0},\ 
  s_z = 1 + \frac{\sigma_z}{j\omega\epsilon_0}
\end{equation}
Several profiles have been suggested for grading $\sigma_d(n)$, The most successfully used one is expressed as
\begin{equation}
  \sigma_d(n) = (l/d)^2\sigma_{d,max}
\end{equation}
where $l$ is the distance apart from the edge of computation domain, and $d = x,y,z$.

In three dimension
\begin{equation}\label{eq:up_d_x_pml}
  j\omega s_y s_z \widetilde{D}_x = c_0 s_x \curlHxThree
\end{equation}
\begin{equation}
  j\omega s_x s_z \widetilde{D}_y = c_0 s_y \curlHyThree
\end{equation}
\begin{equation}
  j\omega s_x s_y \widetilde{D}_z = c_0 s_z \curlHzThree
\end{equation}
\begin{equation}
  j\omega s_y s_z \widetilde{B}_x =-c_0 s_x \curlExThree
\end{equation}
\begin{equation}
  j\omega s_x s_z \widetilde{B}_y =-c_0 s_y \curlEyThree
\end{equation}
\begin{equation}
  j\omega s_x s_y \widetilde{B}_z =-c_0 s_z \curlEzThree
\end{equation}
substituting (\ref{eq:pmlco}) into (\ref{eq:up_d_x_pml}) result in
\begin{equation}
  j\omega
  \left( 1 + \frac{\sigma_y}{j\omega \epsilon_0} \right)
  \left( 1 + \frac{\sigma_z}{j\omega \epsilon_0} \right)\widetilde{D}_x 
  = c_0 \left( 1+\frac{\sigma_x}{j\omega \epsilon_0} \right) \curlHxThree
\end{equation}
Then performing inverse Fourier transform and approximation gives 
\begin{equation}\label{eq:pmlapp}
  \frac{\partial}{\partial t}\widetilde{D}_x + \left( \frac{\sigma_y}{\epsilon_0} + \frac{\sigma_z}{\epsilon_0} \right) \widetilde{D}_x
  = c_0 \left( 1+\int_0^T\frac{\sigma_x}{\epsilon_0} \right) \curlHxThree
\end{equation}
Discretization of (\ref{eq:pmlapp}) leads to
\begin{equation}
  \begin{split}
    \frac{\widetilde{D}_x|^{n+\frac{1}{2}} - \widetilde{D}_x|^{n+\frac{1}{2}}}{\Delta t} &+
    \left( \frac{\sigma_y}{\epsilon_0} + \frac{\sigma_z}{\epsilon_0} \right) \frac{\widetilde{D}_x|^{n+\frac{1}{2}} + \widetilde{D}_x|^{n+\frac{1}{2}}}{2} \\
    &=\frac{c_0}{\Delta x} \left( 1 + \sum_0^T \frac{\sigma_x}{\epsilon_0} \right) curl\_hx
  \end{split}
\end{equation}
and after rearrangement and approximation
\begin{equation}
  \begin{split}
    \widetilde{D}_x|^{n+\frac{1}{2}} &=
    \frac{\displaystyle 1 - \frac{\sigma_y\Delta t}{2\epsilon_0}}{\displaystyle 1 + \frac{\sigma_y\Delta t}{2\epsilon_0}} \cdot \frac{\displaystyle 1 - \frac{\sigma_z\Delta t}{2\epsilon_0}}{\displaystyle 1 + \frac{\sigma_z\Delta t}{2\epsilon_0}} \cdot \widetilde{D}_x|^{n-\frac{1}{2}}\\
    & + \frac{1}{\displaystyle 1 + \frac{\sigma_y\Delta t}{2\epsilon_0}} \cdot \frac{1}{\displaystyle 1 + \frac{\sigma_z\Delta t}{2\epsilon_0}} \cdot 0.5 \left( curl\_hx + \frac{\sigma_x \Delta t}{\epsilon_0}\sum_0^T curl\_hx \right)
  \end{split}
\end{equation}
It would be helpful to define some variables here
\begin{equation}\label{eq:v3}
  v3 = \frac{\displaystyle 1 - \frac{\sigma_d\Delta t}{2\epsilon_0}}{\displaystyle 1 + \frac{\sigma_d\Delta t}{2\epsilon_0}}
\end{equation}
\begin{equation}\label{eq:v2}
  v2 = \frac{1}{\displaystyle 1 + \frac{\sigma_d\Delta t}{2\epsilon_0}}
\end{equation}
\begin{equation}\label{eq:v1}
  v1 = \frac{\sigma_d \Delta t}{\epsilon_0} 
\end{equation}
where $v = i,j,k$ and $d = x,y,z$, and the solution of $\widetilde{D}_x$ can be rewritten as 
\begin{equation}\label{eq:pmldx}
  \widetilde{D}_x|^{n+\frac{1}{2}} = j3 \cdot k3 \cdot \widetilde{D}_x|^{n-\frac{1}{2}} + j2 \cdot k2 \cdot 0.5 \cdot \left( curl\_hx + i1 \cdot \sum_0^T curl\_hx \right)
\end{equation}
The rest five update equations in the UPML region can be derived with similar procedure as
\begin{equation}\label{eq:pmldy}
  \widetilde{D}_y|^{n+\frac{1}{2}} = i3 \cdot k3 \cdot \widetilde{D}_y|^{n-\frac{1}{2}} + i2 \cdot k2 \cdot 0.5 \cdot \left( curl\_hy + j1 \cdot \sum_0^T curl\_hy \right)
\end{equation}
\begin{equation}\label{eq:pmldz}
  \widetilde{D}_z|^{n+\frac{1}{2}} = i3 \cdot j3 \cdot \widetilde{D}_z|^{n-\frac{1}{2}} + i2 \cdot j2 \cdot 0.5 \cdot \left( curl\_hz + k1 \cdot \sum_0^T curl\_hz \right)
\end{equation}
\begin{equation}
  \widetilde{B}_x|^{n+1} = j3 \cdot k3 \cdot \widetilde{B}_x|^{n} - j2 \cdot k2 \cdot 0.5 \cdot \left( curl\_ex + i1 \cdot \sum_0^T curl\_ex \right)
\end{equation}
\begin{equation}
  \widetilde{B}_y|^{n+1} = i3 \cdot k3 \cdot \widetilde{B}_y|^{n} - i2 \cdot k2 \cdot 0.5 \cdot \left( curl\_ey + j1 \cdot \sum_0^T curl\_ey \right)
\end{equation}
\begin{equation}
  \widetilde{B}_z|^{n+1} = i3 \cdot j3 \cdot \widetilde{B}_z|^{n} - i2 \cdot j2 \cdot 0.5 \cdot \left( curl\_ez + k1 \cdot \sum_0^T curl\_ez \right)
\end{equation}





\subsubsection{Reduction to Two Dimensions}
For 2D cases, $\partial / \partial z = 0$ and $s_z = 1$, and the equations becme
\begin{equation}
  j\omega s_y \widetilde{D}_x = c_0 s_x \curlHxTwo
\end{equation}
\begin{equation}
  j\omega s_x \widetilde{D}_y = c_0 s_y \curlHyTwo
\end{equation}
\begin{equation}
  j\omega s_x s_y \widetilde{D}_z = c_0 \curlHzTwo
\end{equation}
\begin{equation}
  j\omega s_y \widetilde{B}_x = c_0 s_x \curlExTwo
\end{equation}
\begin{equation}
  j\omega s_x \widetilde{B}_y = c_0 s_y \curlEyTwo
\end{equation}
\begin{equation}
  j\omega s_x s_y \widetilde{B}_z = c_0 \curlEzTwo
\end{equation}
Following similar steps in deriving 3D equtions, the update equations can be written as
\begin{equation}
  \widetilde{D}_x|^{n+\frac{1}{2}} = j3 \cdot \widetilde{D}_x|^{n-\frac{1}{2}} + j2 \cdot 0.5 \cdot \left( curl\_hx + i1 \cdot \sum_0^T curl\_hx \right)
\end{equation}
\begin{equation}
  \widetilde{D}_y|^{n+\frac{1}{2}} = i3 \cdot \widetilde{D}_y|^{n-\frac{1}{2}} + i2 \cdot 0.5 \cdot \left( curl\_hy + j1 \cdot \sum_0^T curl\_hy \right)
\end{equation}
\begin{equation}
  \widetilde{D}_z|^{n+\frac{1}{2}} = i3 \cdot j3 \cdot \widetilde{D}_z|^{n-\frac{1}{2}} + i2 \cdot j2 \cdot 0.5 \cdot \left( curl\_hz + \sum_0^T curl\_hz \right)
\end{equation}
\begin{equation}
  \widetilde{B}_x|^{n+1} = j3 \cdot \widetilde{B}_x|^{n} - j2 \cdot 0.5 \cdot \left( curl\_ex + i1 \cdot \sum_0^T curl\_ex \right)
\end{equation}
\begin{equation}
  \widetilde{B}_y|^{n+1} = i3 \cdot \widetilde{B}_y|^{n} - i2 \cdot 0.5 \cdot \left( curl\_ey + j1 \cdot \sum_0^T curl\_ey \right)
\end{equation}
\begin{equation}
  \widetilde{B}_z|^{n+1} = i3 \cdot j3 \cdot \widetilde{B}_z|^{n} - i2 \cdot j2 \cdot 0.5 \cdot \left( curl\_ez + \sum_0^T curl\_ez \right)
\end{equation}




\subsection{Periodic Boundary Conditions}
Comparing with PML, PBC is relatively easy to implement.  The best design of PBC is as shown in Fig 2.3 and some
auxiliary arrays surrounding the main domain are added for calculation. These auxiliary arrays copy the values of the
rows or columns in opposed sides and participate in the calculation at the edges they are located. This is just the
original idea of how to create a fake view of infinite continuous periodic domain for calculating, which can be used by
the design of Parallelization: by sending the row or column at the edge to adjacent calculation domains of MPI to be
their auxiliary array, the feature of parallelization can be completed.

