\cleardoublepage
\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{999}

  \bibitem
  {}
  Alsunaidi, M. A., Ahmad A. AI-Jabr,
  ``A General ADE-FDTD Algorithm for the simulation of Dispersive Structures'',
  \textit{IEEE Photonics Tech. Lett.},
  vol. 21,
  pp. 817-819,
  2009

  \bibitem
  {}
  Bernard, L., Ruben Rodriguez Torrodo, and Lionel Pichon,
  ``Efficient Implementation of the UPML in the Generalized Finite-Difference Time-Domain Method'',
  \textit{IEEE Trans. Magnetics},
  vol. 46,
  pp. 3492-3495,
  2010

  \bibitem
  {}
  Byelobrov, O. B., Trevor M. Benson, Jiri Ctyroky, Ronan Sauleau, and Alexander I. Nosich,
  ``Plasmon and Structure Resonances in the Scattering of Light by a Periodic Chain of Silver Nanocylinders'',
  \textit{IEEE ICTON},
  pp. 1-3,
  2010

  \bibitem
  {cheng}
  Cheng, D. K.,
  \textit{Field and Wave Electromagnetics}, second edition,
  Addison Wesley,
  1989

  \bibitem
  {}
  Cubukcu, E., Federico Capasso,
  ``Optical nanorod antennas as dispersive one-dimensional Fabry-Perot resonators for surface plasmons'',
  \textit{Appl. Phys. Lett.},
  vol. 95,
  201101,
  2009

  \bibitem
  {}
  Davidson, D. B.,
  \textit{Computational Electromagnetics for RF and Microwave Engineering}, second edition,
  Cambridge University Press,
  2005

  \bibitem
  {}
  Demir, V., Atef Z. Elsherbeni and Ercument Arvas,
  ``FDTD formulation for Dispersive Chiral Media Using the Z Transform Method'',
  \textit{IEEE Trans. Antennas Propagat.},
  vol. 53,
  pp. 3374-3384,
  2005

  \bibitem
  {}
  Ding, P. P., Gaofeng Wang, Hai Lin, and Bing-Zhong Wang,
  ``Unconditionally Stable FDTD Formulation With UPML-ABC'',
  \textit{IEEE Microsave and Wireless Components Lett.},
  vol. 16,
  pp. 161-163,
  2006

  \bibitem
  {}
  Fu, J. H., Fan-Yi Meng, Guo-Hui Yang, and Qun Wu,
  ``Analysis of The Double Negative Metamaterials using FDTD'',
  \textit{Microwave Opt. Tech. Lett.},
  vol. 50,
  pp. 1411-1414,
  2008

  \bibitem
  {}
  Gamma, E., Richard Helm, Ralph Johnson, and John Vlissides,
  \textit{Design Patterns: Elements of Reusable Object-Oriented Software},
  Addison-Wesley Professional,
  1994

  \bibitem
  {}
  Garc\'\i{}a-Vidal, F. J., H. J. Lezec, T. W. Ebbesen, adn L. Mart\'\i{}n-Moreno,
  ``Multiple Paths to Enhance Optical Transmission through a Single Subwavelength Slit'',
  \textit{Phys. Rev. Lett.},
  vol. 90,
  213901,
  2003

  \bibitem
  {}
  Harrington, R. F.,
  \textit{Time-Harmonic Electromagnectic Fields (reissued)},
  Wiley-IEEE Press,
  2001

  \bibitem
  {}
  Kawaguchi, H., Yuya Fujita, Yoshiyuki Fujishima and Shun-suke Matsuoka,
  ``Improved Architecture of FDTD/FIT Dedicated Computer for Higher Performance Computation'',
  \textit{IEEE Trans. Magnetics},
  vol. 44,
  pp. 1226-1229,
  2008

  \bibitem
  {}
  Kelley, D. F., R. J. Luebbers,
  ``Piecewise Linear Recursive Convolution for Dispersive Media Using FDTD'',
  \textit{IEEE Trans. Antennas Propagat.},
  vol. 44,
  pp. 792-797,
  1996

  \bibitem
  {}
  Li, D., Costas D. Sarris,
  ``FDTD Lattice Termination with Periodic Boundary Conditions'',
  \textit{IEEE ICMSD},
  pp. 329-332,
  2009

  \bibitem
  {}
  Maier, S. A.,
  \textit{Plsmonics: Fundamentals and Applications},
  Springer,
  2007

  \bibitem
  {}
  Mateus, C. F. R., Michael C. Y. Huang, Yunfei Deng, Andrew R. Neureuther and Connie J. Chang-Hasnain,
  ``Ultrabroadband Mirror Using Low-Index Cladded Subwavelength Grating'',
  \textit{IEEE Photonics Tech. Lett.},
  vol. 16,
  pp. 518-520,
  2004

  \bibitem
  {}
  Mao, Y., Chaomeng Zhou and Jian Zhang,
  ``Implementation of UPML for Weakly Conditionally Stable FDTD in Periodic Structures'',
  \textit{IEEE ICUWB},
  pp. 1-3,
  2010

  \bibitem
  {}
  Ng, N. Y., Wei-Chih Liu,
  ``Local-field confinement in three-pair arrays of metallic nanocylinders'',
  \textit{Opt. Exp.},
  vol. 14,
  pp. 4504-4513,
  2006

  \bibitem
  {}
  Palik, E. D.,
  \textit{Handbook of Optical Constants of Solids},
  Academic Press,
  1997

  \bibitem
  {}
  Pozar, D. M.,
  \textit{Microwave Engineering}, third edition,
  Wiley,
  2004

  \bibitem
  {rao} 
  Rao, N. N.
  \textit{Elements of Engineering Electromagnetics}, sixth edition,
  Prentice Hall,
  2004

  \bibitem
  {}
  Rosenberg, J., Rajeev V. Shenoi, Thomas E. Vandervelde, Sanjay Krishna, and Oskar Painter,
  ``A multispectral and polarization-selective surface-plasmon resonant midinfrared detector'',
  \textit{Appl. Phys. Lett},
  vol. 95,
  161101,
  2009

  \bibitem
  {}
  Saleh, B. E., Malvin Carl Teich
  \textit{Fundamentals of Photonics}, second edition,
  Willy-Interscience,
  2007

  \bibitem
  {sebesta}
  Sebesta, R. W.,
  \textit{Concepts of Programming Languages}, eighth edition,
  Addison Wesley,
  2007

  \bibitem
  {}  
  Shibayama, J., Ryoji Ando, Akifumi Nomura, Junji Yamauchi and Hisamatsu Nakano,
  ``Simple Trapezoidal Recursive Convolution technique for the Frequency-Dependent FDTD Analysis of a Drude-Lorentz Model'',
  \textit{IEEE Photonics Tech. Lett.},
  vol. 21,
  pp. 100-102,
  2009

  \bibitem
  {}
  Sullivan, D. M.,
  ``A Simplified PML for Use with the FDTD method'',
  \textit{IEEE Microwave Guided Wave Lett.},
  vol. 6,
  pp. 97-99,
  1996

  \bibitem
  {}
  Sullivan, D. M.,
  ``An Unsplit Step 3-D PML for Use with the FDTD Method'',
  \textit{IEEE Microwave Guided Wave Lett.}, 
  vol. 7,
  pp. 184-187,
  1997

  \bibitem
  {taflove}
  Taflove, A., Susan C. Hagness, 
  \textit{Computational Electrodynamics: The Finite-Difference Time-Domain Method}, third edition,
  Artech House,
  2005

  \bibitem
  {}
  Todorov, Y., L. Tosetto, J. Teissier, A. M. Andrews, P. Klang, R Colombelli, I Sagnes, G. Strasser and C. Sirtori
  ``Optical properties of metal-dielectric-metal microcavities in the THz frequency range'',
  \textit{Opt. Exp.},
  vol. 18,
  pp. 13866-13907,
  2010

  \bibitem
  {}
  Wait, J. R.,
  ``Scattering of A Plane Wave from Circular Dielectric Cylinder at Oblique Incidence'',
  \textit{Can. J. Phys.}
  vol. 33,
  pp. 189-195,
  1955

  \bibitem
  {}
  Wei, Q., S. Crozier, L. Xia and F. Liu,
  ``Object-Oriented Designed Finite-difference Time-domain Simulator for Electromagnetic Analysis and Design in MRI'',
  \textit{IEEE EMBS},
  pp. 1116-1119,
  2004

  \bibitem
  {}
  Yariv, A., Pochi Yeh,
  \textit{Photonics: Optical Electronics in Modern Communications}, sixth edition,
  Oxford University Press, 
  2007

\end{thebibliography}
