\section{examination}
The surface plasmonic structures become popular in this two decades owing to plasmonic waveguides admit optical waves
transmitting in subwavelength structures having metal-dielectric interfaces specially in nano-scale. The conduction
electrons oscillate in the longitudinal direction and the Maxwell's equations show the solution is electromagnetic
fields confined near the interface of metal.

Single silver rod may one of the most simple metal-dielectric interface. Phasor distribution of single silver rod is
easy to obtain via frequency domain method such as Multiple-Scattering method. By performing Fourier transform on
timeline of FDTD result reaching steady state, a good approximation is expected. To ensure the yaFDTD framework to carry
out a credible result, comparison result between exact solution and FDTD is a good index.

The example here is a nano cylinder with radius 25 nm. The cylinder material is silver simulated using Drude Model
with following parameters: $\epsilon_r = 8.926$, $\omega_p = 9.39 \times 10^{15}$ rad/s, and $\gamma_p = 3.14 \times
10^{13}$ rad/s.  There would be one more thing remarkable before starting simulation to acquire better result. Although
the UPML has excellent performance for absorbing propagatin waves; however, the evanescent waves still grows field
intensity up inside the UPML. To prevent the reflection from PML interact with the scatters. It need extra space between
PML and scatters. Here we set the grid size to be 1 nm and make whole space being 500 nm $\times$ 500 nm.

Final arrangement is shown in Fig 4.1. Plane wave in $\mathrm{TE_z}$ mode is impinged in x-direction with wavelength
347.5 nm. Fig 4.2 shows the Re\{$H_z$\} profiles of phasor distribution when reaching steady state after 100 periods of
plane wave. Fig 4.3 shows the exact solution of Re\{$H_z$\} profiles. and numerical error shown in Fig 4.4 is calculated
by subtracting the result from FDTD with the result from exact solution. The inaccuracy is small than 0.1 with the
simplest Stair-Case scheme. In general, it good enough to apply the framework on more complex cases.
